\documentclass{article}
\usepackage[left = 3cm, right = 3cm]{geometry}

\usepackage[normalem]{ulem}
\usepackage[colorlinks=false]{hyperref}
\renewcommand\UrlFont{\normalfont\ttfamily\underline}

\begin{document}
\begin{Huge}
\noindent Sheng Xu
\end{Huge}

\vspace{5mm}
\begin{minipage}{0.5\linewidth}
  \flushleft
\noindent 213 Fine Hall, Princeton University \\
\noindent Washington Rd \\
\noindent Princeton, NJ 08544-1000
\end{minipage}
\hfill
\begin{minipage}{0.35\linewidth}
  Phone: 410-868-9529 \\
  Email: sxu21@princeton.edu \\
  Homepage: https://sx67.github.io/
\end{minipage}

\vspace{5mm}
\begin{large}
\noindent \textbf{Academic Appointment}
\end{large}
\vspace{5mm}

\begin{minipage}{0.65\linewidth}
\noindent {\bf Princeton University}\\
Postdoctoral Researcher\\
Advisor: Amit Singer\\
\end{minipage}\hfill
\begin{minipage}{0.34\linewidth}
\flushright
2022 - present\\
Princeton, NJ, USA\\
\end{minipage}


\vspace{5mm}
\begin{large}
\noindent \textbf{Education}
\end{large}
\vspace{5mm}





\begin{minipage}{0.65\linewidth}
\noindent {\bf Yale University}\\
Ph.D. in Statistics and Data Science\\
\end{minipage}\hfill
\begin{minipage}{0.34\linewidth}
\flushright
2016 - 2022\\
New Haven, CT, USA\\
\end{minipage}
\vspace{-6mm}
\begin{itemize}
\setlength{\itemsep}{-0.5mm}
\item[\raisebox{0.25ex}{\tiny$\bullet$}] Advisors: Zhou Fan and Sahand Negahban
\item[\raisebox{0.25ex}{\tiny$\bullet$}] Thesis: ``Efficient Estimation of Signals via Non-Convex Approaches''
\item[\raisebox{0.25ex}{\tiny$\bullet$}] Francis J. Anscombe Award: “Given on an occasional basis for outstanding academic performance in the Department of Statistics and Data Science.”
\end{itemize}

\begin{minipage}{0.65\linewidth}
\noindent {\bf Peking University}\\
B.S. in Mathematics\\
Advisor: Zhi Geng\\
B.S. (dual) in Economics\\
Advisor: Miaojie Yu\\
\end{minipage}\hfill
\begin{minipage}{0.34\linewidth}
\flushright
2010 - 2014\\
Beijing, China\\
2011 - 2014\\
Beijing, China\\
\end{minipage}







% \vspace{2mm}
% Lecturer, Complementary Session for Statistics 210B, Spring 2016.

% \hspace{4mm} Self-prepared weekly lectures, covering learning theories, concentration inequalities, 

% \hspace{4mm} high dimensional geometry, sparse linear regression, compressed sensing and kernel theories.

\vspace{5mm}
\begin{large}
\noindent \textbf{Research Experiences}
\end{large}
\vspace{5mm}

\begin{large}
\noindent Research Interests
\end{large}



\begin{itemize}

\item Theory / Methodology: statistical inference; machine learing; mathematics of data science; optimization (with emphasis on non-convex landscapes).

\item Applications: signal and image processing (notably 3-D reconstruction in cryogenic electron microscopy (Cryo-EM)); structural biology; geophysics; network analysis; time series analysis; econometrics.

\end{itemize}

\vspace{3mm}

\begin{large}
\noindent Journal Publications
\end{large}

\begin{enumerate}
\item Gong, Z., Evans, D.A.D., Fu, R.R., \textbf{Xu, S.} (2025). \href{https://www.sciencedirect.com/science/article/pii/S0012821X25003061?casa_token=vsDDryHMXpEAAAAA:lIHeM20Me4SpR5t_JPjA19SuDL339acc9p_Q5RUpptXcb5T5sLdaQLNYuMtuzefqHPEpawJzSxhK}{Reassessing the Geocentric-Axial-Dipole (GAD) Model for Proterozoic Time with Paleomagnetic Directions from Dike Swarms.} \emph{Earth and Planetary Science Letters (EPSL)}, 667: 119508.

\item Fan, Z., Lederman, R., Sun, Y., Wang, T., \& \textbf{Xu, S.} (2024). \href{https://projecteuclid.org/journals/annals-of-statistics/volume-52/issue-1/Maximum-likelihood-for-high-noise-group-orbit-estimation-and-single/10.1214/23-AOS2292.full}{Maximum Likelihood for High-Noise Group Orbit Estimation and Single-Particle Cryo-EM.} \emph{Annals of Statistics}: 52(1), 52-77.



\item Gao, W. Y., Li, M., \& \textbf{Xu, S.} (2023). \href{https://www.sciencedirect.com/science/article/pii/S0304407622000884}{Logical Differencing in Dyadic Network Formation Models with Nontransferable Utilities.} \emph{Journal of Econometrics}, 235(1): 302-324.

\item \textbf{Xu, S.}, \& Fan, Z. (2021). \href{https://academic.oup.com/jrsssb/article/83/2/271/7056035}{Iterative Alpha Expansion for Estimating Gradient-Sparse Signals from Linear Measurements.} \emph{Journal of the Royal Statistical Society: Series B (JRSS-B)}, 83(2): 271-292.

\item Han, F., \textbf{Xu, S.}, \& Zhou, W. (2018). \href{https://projecteuclid.org/journals/bernoulli/volume-24/issue-3/On-Gaussian-comparison-inequality-and-its-application-to-spectral-analysis/10.3150/16-BEJ912.full}{On Gaussian Comparison Inequality and Its Application to Spectral Analysis of Large Random Matrices.} \emph{Bernoulli}, 24(3): 1787-1833.
\end{enumerate}


\begin{large}
\noindent Conference Publications
\end{large}

\begin{enumerate}
\item Chen, L., \& \textbf{Xu, S.} (2021). \href{https://openreview.net/forum?id=vK9WrZ0QYQ}{Deep Neural Tangent Kernel and Laplace Kernel Have the Same RKHS.} In \emph{Proceedings of the 9th International Conference on Learning Representations (ICLR)}.
\item \textbf{Xu, S.}, Fan, Z., \& Negahban, S. (2020). \href{https://proceedings.mlr.press/v125/xu20a.html}{Tree-Projected Gradient Descent for Estimating Gradient-Sparse Parameters on Graphs.} In \emph{Proceedings of the 33rd Annual Conference on Learning Theory (COLT)}.
\item Qiu, H., \textbf{Xu, S.}, Han, F., Liu, H., \& Caffo, B. (2015). \href{https://proceedings.mlr.press/v37/qiu15.html}{Robust Estimation of Transition Matrices in High Dimensional Heavy-Tailed Vector Autoregressive Processes.} In \emph{Proceedings of the 32nd International
Conference on Machine Learning (ICML)}.
\end{enumerate}



\begin{large}
\noindent Preprints / Submitted Manuscripts
\end{large}

\begin{enumerate}

\item \textbf{Xu, S.}, Zhang, A. Y., \& Singer, A. (2025). \href{https://arxiv.org/abs/2509.22945}{Misspecified Maximum Likelihood Estimation for Non-Uniform Group Orbit Recovery.} Submitted to \emph{Journal of the American Statistical Association (JASA)}.

\item Kileel, J., Mickelin, O., Singer, A., \& \textbf{Xu, S.} (2025). Method of Double Moments for 3-D Reconstruction in Cryo-EM: Using Multiple Datasets with Different Viewing Angle Distributions. Submitted to \emph{Inverse Problems}.

\item \textbf{Xu, S.}, Balanov, A., Singer, A., Bendory, T. (2025). \href{https://arxiv.org/abs/2412.03723}{Bayesian Perspective for Orientation Determination in Cryo-EM with Application to Structural Heterogeneity Analysis.} Under revision at \emph{Acta Crystallographica Section D: Structural Biology}.

\item Zhang, L., Mickelin, O., \textbf{Xu, S.}, \& Singer, A. (2025). \href{https://arxiv.org/abs/2507.20459}{Diagonally-Weighted Generalized Method of Moments Estimation for Gaussian Mixture Modeling.} Under revision at \emph{SIAM Journal on Mathematics of Data Science (SIMODS)}.


\item Gao, W. Y., \textbf{Xu, S.}, \& Xu, K. (2025). \href{https://arxiv.org/abs/2009.02854}{Two-Stage Maximum Score Estimator.} Submitted to \emph{Bernoulli}.
\end{enumerate}


\begin{large}
\noindent Manuscripts in Preparation
\end{large}

\begin{enumerate}
\item \textbf{Xu, S.}, Sharon, N., Storey, J., Singer, A. (2025). Distribution-Free Symmetry Detection in Multi-Reference Alignment. 

\item \textbf{Xu, S.}, Fan, Z., \& Negahban, S. (2025). On Convergence of Frequency Marching
Algorithm for Multi-Reference Alignment. 

\item \textbf{Xu, S.}, \& Cattaneo, M. (2025). Adaptive Minimax Estimation of Quadratic Functionals under Dyadic Data.

\item Zhang, A., Mickelin, O., \textbf{Xu, S.}, \& Singer, A. (2025) Autocorrelation Analysis for Reconstruction in Cryo-EM with Structural Priors.

\end{enumerate}


\begin{large}
\noindent Patents
\end{large}

\begin{enumerate}
\item \textbf{Xu, S.}, Zhang, Y., Singer, A. \emph{``Unbiased 3-D Reconstruction in Cryo-Electron Microscopy via Anisotropic Viewing-Angle Prior''}. U.S. Provisional Patent Application No. 63/887,219. Filed September 2025.

\item Kileel, J., Mickelin, H.E.O., Singer, A., \textbf{Xu, S.} \emph{``Method of Moments for 3-D Reconstruction in Cryo-Electron Microscopy from Multiple Datasets with Different Viewing Angle Distributions''}. U.S. Provisional Patent Application No. 63/816,313. Filed June 2025.
\end{enumerate}



\begin{large}
\noindent Software
\end{large}

\begin{enumerate}

\item $\mathsf{MoDM}$: $\mathsf{Python}$ package implementing the Method of Moments for 3-D reconstruction in cryo-EM from two datasets with different viewing angle distributions (on github).

\item $\mathsf{ITALE}$: $\mathsf{R}$ package for piecewise-constant signal estimation on general graphs (on github).

\end{enumerate}


\vspace{5mm}
\begin{large}
\noindent \textbf{Teaching Experiences}
\end{large}
\vspace{5mm}

Instructor, Princeton University, APC 199/MAT 199, Math Alive, Spring 2025.

\vspace{2mm}

Co-organizer, Princeton University, Junior Seminar in Mathematics, Top 10 Algorithms of the 20th Century, Fall 2024.

\vspace{2mm}

Instructor, Princeton University, APC 199/MAT 199, Math Alive, Spring 2024.

\vspace{2mm}
TA, Yale University, S\&{DS} 351/551, Stochastic Processes, Spring 2022 (taught by Andrew, Barron). 

\vspace{2mm}
TA, Yale University, S\&{DS} 363/563, Multivariate Statistics, Spring 2020 (taught by Jonathan, Reuning-Scherer). 

\vspace{2mm}
TA, Yale University, S\&{DS} 410/610, Statistical Inference, Fall 2019 (taught by Zhou, Fan). 

\vspace{2mm}
TA, Yale University, S\&{DS} 351/551, Stochastic Processes, Spring 2019 (taught by Sahand, Negahban and Yihong, Wu). 

\vspace{2mm}
TA, Yale University, S\&{DS} 410/610, Statistical Inference, Fall 2018 (taught by Zhou, Fan). 

\vspace{2mm}
TA, Yale University, S\&{DS} 351/551, Stochastic Processes, Spring 2018 (taught by Sahand, Negahban). 



\vspace{5mm}
\begin{large}
\noindent \textbf{Professional Services}
\end{large}
\vspace{5mm}

\begin{large}
\noindent Talks
\end{large}


\vspace{2mm}
University of Missouri, Data Seminar, Columbia, MO, 2025


\vspace{2mm}
AMS Spring Eastern Sectional Meeting, Hartford, CT, 2025

\vspace{2mm}
SIAM Conference on Mathematics of Data Science, Atalanta, GA, 2024


\vspace{2mm}
New Jersey Institute of Technology, Statistics Seminar, Newark, NJ, 2024.

\vspace{2mm}
Joint Statistical Meetings (JSM), Portland, OR, 2024.

\vspace{2mm}
National University of Singapore, IMS Young Mathematical Scientists Forum---Statistics and Data Science, Singapore, 2023.

\vspace{2mm}
Princeton University, PACM IDeAS Seminar, Princeton, NJ, 2021.

\vspace{2mm}
Conference on Learning Theory (COLT), Virtually (due to COVID), 2020.

\vspace{2mm}
International Conference on Machine Learning (ICML), Lille, France, 2015.



\vspace{2mm}

\begin{large}
\noindent Reviewing
\end{large}

\vspace{2mm}
\textbf{Journals:} Annals of Statistics (AoS), Annals of Applied Statistics (AoAS), Bernoulli, Journal of Econometrics (JoE), IEEE Transactions on Information Theory, SIAM Journal on Mathematics of Data Science (SIMODS).


\vspace{2mm}
\textbf{Conferences:} 


\vspace{2mm}
\quad\quad  Conference on Neural Information Processing Systems (NeurIPS), 2021, 2022, 2023, 2025.

\vspace{2mm}
\quad\quad AAAI Conference on Artificial Intelligence (AAAI), 2025.

\vspace{2mm}
\quad\quad International Conference on Learning Representations (ICLR), 2021.

\vspace{2mm}
\quad\quad International Conference on Machine Learning (ICML), 2020.





% \vspace{5mm}
% \begin{large}
% \noindent \textbf{Courses}
% \end{large}

% \begin{enumerate}
% \item Fall, 2014: STAT205A (Probability Theory): A+; STAT210A (Theoretical Statistics): A+; 

% \hspace{1.62cm} STAT215A (Applied Statistics): A+.
% \item Spring, 2015: STAT205B (Probability Theory): A+; STAT210B (Theoretical Statistics): A+; 

% \hspace{2.05cm} EE227C (Convex Optimization): A.
% \item Fall, 2015: EE229A (Information Theory and Coding): A+; 

% \hspace{1.62cm} STAT212A (Multiple Testing and Selective Inference): A+.
% \item Spring, 2016: EE229B (Error Control Coding): A.

% \item Fall, 2016: STAT241A (Statistical Learning): A; 

% \hspace{1.62cm} STAT240 (Nonparametric and Robust Methods): A+.
% \end{enumerate}

\end{document}


%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:
